Computing in the Field of Rationals

### 2012-06-18 rational_ext.tex

>>>>

\roshan{We need to prove this. I am not sure how to start.}
\begin{proposition}[Strong Normalizing]
\label{prop:termination-piee-plus} 
Computations in {{langRev}} extended with {{eta+}} and {{eps+}} are
always terminating.
\end{proposition}

\roshan{This is straightforward.}
\begin{proposition}[Strong Normalizing]
\label{prop:termination-piee-times} 
Computations in {{langRev}} extended with {{eta*}} and {{eps*}} are
always terminating.
\end{proposition}

\begin{proposition}[Weak Normalizing]
\label{prop:termination-piee} 
Computations in full {{langRevEE}} are weak normalizing.
\end{proposition}

\begin{center}
  \includegraphics{diagrams/inf1.pdf}
\end{center}

\subsection{Logical Reversibility}

\begin{proposition}[Logical Reversibility]
{{langRev}} with {{eta+}} and {{eps+}} is logically reversible.
\end{proposition}
\roshan{Proof follows from compilation to {{langRevT}} }

\begin{proposition}[Logical Reversibility]
{{langRev}} with {{eta*}} and {{eps*}} is logically reversible.
\end{proposition}

This is an awkward one. I dont thnk that the above statement is
right.. At least not in the usualy sense. We can construct the
following combinators.

{{c1 : bool <-> bool}}

{{c1 true |--> {[true, false ]} }}

{{c1 false |--> {[true, false ]} }}

{{c1{dagger} true |--> {[true, false ]} }}

{{c1{dagger} false |--> {[true, false ]} }}

\noindent
And

{{c2 : bool <-> bool}}

{{c2 true |--> {[true, false ]} }}

{{c2 false |--> undefined }}

{{c2{dagger} true |--> true }}

{{c2{dagger} false |--> true }}

Probably the right way to approach this is to see what they do in
physics. If fractionals do correspond to measurement and the
categorical structures of Coecke and Abramsky, then the ideas of
reversibility in that setting should also apply here.

I don't think this issue will go away by any sort of choice of
top-level. I tried to design a top-level that can fix this -- I dont
think it is possible.
